### 2020-08-20 ReadMe.rmd
updates

**Most of the figures in the thesis are reproducible**. This repo is set up for continuous deployment of a [github page](https://vlucet.github.io/landchange-connectivity-monteregie/) that contains the main figures in the thesis.

@@

  - Run docker image (`docker run [options] vlucet/land_con_monteregie:3.6.2-1 /bin/bash && cd ~/land_con_monteregie`), executing a command that starts bash and move to the repo directory (`/bin/bash && cd ~/land_con_monteregie`), with options to run an interactive terminal (`-it`) with authentification disabled (` DISABLE_AUTH=true`).

@@

  - Run docker image with rstudio in your browser (see [this post](https://ropenscilabs.github.io/r-docker-tutorial/02-Launching-Docker.html) for another example). Here you run the container in a detached mode (`-d`) on a local port (`-p 8787:8787`). Then, go to `http://192.168.99.100:8787` in your browser to access Rstudio.

@@

#### Detailed workflow

The workflow of the thesis is made up mainly of `R` scripts, but also makes use of a few `Julia`and `Python` scripts. The entire thesis analysis and be easily re-run (providing that you have all the necessary data) with the help of the main bash utility [`landcon.sh`](https://github.com/VLucet/landchange-connectivity-monteregie/blob/master/landcon.sh) in the top directory. This utility is used to run all the steps in the thesis analysis. Help can be acessed with `landcon.sh -h`

@@

Usage: [-p prep] [-m model no prep] [-a run all] [-f fit & predict]
       [-s stsim] [-r reclassify] [-c circuitscape] [-d post process] [-g make figures]
```

>>>>

**Most of the figures in the thesis are reproducible**. This repo is set up for continuous (daily) deployment of a [github page](https://vlucet.github.io/landchange-connectivity-monteregie/) that contains the main figures of the thesis.

@@

  - **Run docker image interactively** (`docker run [options] vlucet/land_con_monteregie:3.6.2-1 /bin/bash && cd ~/land_con_monteregie`), executing a command that starts bash and move to the repo directory (`/bin/bash && cd ~/land_con_monteregie`), with options to run an interactive terminal (`-it`) with authentification disabled (` DISABLE_AUTH=true`).

@@

  - **Run docker image with rstudio in your browser** (see [this post](https://ropenscilabs.github.io/r-docker-tutorial/02-Launching-Docker.html) for another example). Here you run the container in a detached mode (`-d`) on a local port (`-p 8787:8787`). Then, go to `http://192.168.99.100:8787` in your browser to access Rstudio.

@@

Note that with docker, you have the option to [link a local volume](https://docs.docker.com/storage/volumes/).

#### Reproducing figures

The workflow is controlled with the help of the main bash utility [`landcon.sh`](https://github.com/VLucet/landchange-connectivity-monteregie/blob/master/landcon.sh) in the top directory. This utility is used to run all the steps in the thesis analysis. Help can be acessed with `landcon.sh -h`

@@

Usage: landcon.sh [-a run all] [-p prep] [-m model no prep] [-f fit & predict]
                  [-s stsim] [-r reclassify] [-c circuitscape] [-d post process] [-g make figures]

Subcommands: prep, fitpred, stsim, cs, figs (use -h to see usage on each subcommand)
```

**In order to reproduce the main figures of the thesis**, simply run:

```{}
./landcon.sh -g
```

#### Detailed thesis workflow
